---
title: "Homework 6"
auhor: "Tongtong Zhu"
date: "2022-12-1"
output: github_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Problem 1

### Load dataset

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Bootstrap for r square and log value 

```{r}
boot_straps = 
  weather_df %>%
  bootstrap(n = 100, id = "strap_num") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    results_r = map(models, broom::glance),
    results_log = map(models, broom::tidy)
  ) %>% 
  unnest(results_r,results_log) %>% 
  select(strap_num, term, estimate, r.squared) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate) %>% 
  rename(
    beta_0 = "(Intercept)",
    beta_1 = "tmin"
  ) %>% 
  mutate(
    log_beta = log(beta_0*beta_1)
  ) %>% 
  select(strap_num, r.squared, log_beta)
  
```

### Distribution of r square

```{r}
boot_straps %>% 
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(
    title = "Distribution of r squared estimates",
    x = "r squared estimate"
  )
  
```

**Description of r squared estimates** 

This distribution of r squared estimates appears to follow a normal distribution, centered around 0.905.

### Distribution of log beta product

```{r}
boot_straps %>% 
  ggplot(aes(x = log_beta)) +
  geom_density() +
  labs(
    title = "Distribution of log(beta0*beta1) estimates",
    x = "log(beta0*beta1)"
  )
  
```

**Description of log beta product**

This distribution of log beta product appears to follow a normal distribution, centered around 2.02.



